### 2016-12-19 experiments.tex
more fixes and such

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our hypotheses.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.   If the {\tt jsfunfuzz} produced test case executes to the end and prints {\tt TEST SUCCESSFULLY COMPLETED} it is considered successful.  This is only a moderately strong oracle, and allows serious deviations in behavior from both the JavaScript language specification and normal SpiderMonkey behavior, while constraining other aspects of execution fairly tightly, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely.  The only weakness is that there is no check on speed of or time to produce compiled code.

@@

In order to check whether the improvement is statistically reliable for SpiderMonkey 1.6 faults, we sliced the PLDI 13 tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets (about 90 tests, with a mean of just over 10 distinct faults) 2.85\% better than the mean APFD for the PLDI 13 metric (86.76\%), and the result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for PLDI 13's best metric.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build (used to produce our compiled versions for repair checks), compiled hello world correctly, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve is worse compared to the PLDI 2013 curve.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage provides only 16 faults over 31 tests.

For GCC wrong code faults, the baseline chance two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a fault lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric matched fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- running in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    The mean and median homogeneity (\% of repaired tests corresponding to most common repaired fault) were 79.4\% and 100\%, respectively.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0 wrong code faults.  For the same reasons as with SpiderMonkey, only some faults were deemed to have a strong enough ground truth patch for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but this was one of only two useful localizations.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed extremely well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  For the MUSEUM data set, there are no cases with multiple faults for our method to use to further distinguish repairs, so its similarity to MUSEUM in results is not surprising (in this context, our approach is essentially MUSEUM modified to throw out any repairs that cause previously passing tests to fail).

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average.  These executions can obviously be performed in parallel, on low-cost virtual machines in the cloud.  The cost is further reduced by a few more facts: most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  
\begin{comment}
Keeping hot mutants for a heavily modified program could be costly (since each mutant must be recompiled, if not re-tested, for each modification to the code), but for stable releases this is a simple approach to keep costs low.
\end{comment}

>>>>

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our hypotheses.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.  This is only a moderately strong oracle, and allows serious deviations from both the JavaScript language specification and normal SpiderMonkey behavior, while checking some complex details, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely --- only missed optimizations are allowed.

@@

In order to check our results statistically, we sliced the PLDI 13 tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets that was 2.85\% better than the mean APFD for the PLDI 13 metric (86.76\%), over sets of $\sim 10$ faults. The result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for PLDI 13's best metric.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve is worse compared to the PLDI 2013 curve.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage provides only 16 faults over 31 tests.

For GCC wrong code faults, the baseline chance two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a fault lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric matched fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- running in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0.  Again, only some faults were deemed to have a strong enough ground truth patches for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but usually performed poorly.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed very well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists, and results in {\bf Repair} either providing a ``useful'' localization or no localization at all, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  For the MUSEUM data set, there are no cases with multiple faults for our method to use to further distinguish repairs, so its similarity to MUSEUM in results is not surprising (in this context, our approach is essentially MUSEUM modified to throw out any repairs that cause previously passing tests to fail).

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  
\begin{comment}
Keeping hot mutants for a heavily modified program could be costly (since each mutant must be recompiled, if not re-tested, for each modification to the code), but for stable releases this is a simple approach to keep costs low.
\end{comment}

### 2016-12-19 introduction.tex
Alex ready
more fixes and such

The goal of this paper, an effective metric for computing distance between program executions (in particular, failing test cases), is motivated in large part by progress in automated testing.  Recent advances, some implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in, e.g., modern optimizing compilers\footnote{In this paper, we take the problem of testing and debugging compilers as representative of the general problem of testing and debugging complex critical systems software.}.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of program mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. The approach suggests a plausible metric for comparing any two program executions, not just failing test cases.  Comparing executions has been a prominent concept in dynamic analysis throughout much of the last two decades \cite{NearNeighbor,Sumner2011} (e.g., Ball's early discussion of profile similarity \cite{BallConcept}).

@@

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one fault; then re-run all tests, knowing that the remaining failures are due to unfixed faults, repeating until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 11/20/2015, LLVM clang had 89 bugs assigned but not resolved, some dating to 2008.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing these problems is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, producing more open problems.   High priority faults may be hidden by stubborn low-priority faults.

@@

\subsection{The Onion-Ring and Causality}

These hypothesis do not claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is certainly some level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Characterizing the granularity of program mutants is likely difficult, but fortunately it is not necessary.

@@

\subsection{Contributions}

>>>>

The goal of this paper, an effective metric for computing distance between program executions (in particular, failing test cases), is motivated in large part by progress in automated testing.  Recent advances, some implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in, e.g., modern optimizing compilers\footnote{We claim testing/debugging complex systems software is well represented by compiler testing as an instance.}.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of program mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. The approach suggests a plausible metric for comparing any two program executions, not just failing test cases.  Comparing executions has been a prominent concept in dynamic analysis throughout much of the last two decades \cite{NearNeighbor,Sumner2011} (e.g., Ball's early discussion of profile similarity \cite{BallConcept}).

@@

Automated test generators tend to produce many failures, which correspond to far fewer faults.  The distribution of faults in a set of failures tends to follow a strong power-law curve, where a few faults account for most failures, and many or even most faults have only 1 or 2 associated failures (even in a set of 1,000 or more test cases) \cite{PLDI13}.  Looking at all the failures to find  distinct faults is impractical.  It is also impractical to apply the iterative approach:  first, fix one test's fault; then re-run all tests, until all tests pass.  There may be some (possibly known) faults that are very difficult to fix. As of 11/20/2015, clang had 89 unresolved, assigned bugs, some dating to 2008.  Knowing if a randomly generated test case is an instance of a known failure can be difficult, and fixing these problems is unlikely.    A research group with a novel fault-detection technique \cite{csmith,ISSTA12,ZhendongPLDI} may dump dozens of new faults on a project at once, and high priority faults may be hidden by stubborn low-priority faults.

@@

%\subsection{The Onion-Ring and Causality}

These hypothesis do not claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is certainly some level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

@@

%\subsection{Contributions}

### 2016-12-19 localizations.tex
more fixes and such

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failng test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.

>>>>

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failng test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.  One possible
advantage of this approach, unique to our knowledge, is that by
ranking \emph{mutants} the localization offers developers not simply a
ranked statement but a kind of ``explanation'' of the fault:  if this
mutant were applied, the fault would not exhibit.  As Kochhar et
al. show \cite{Kochhar}, a large majority (more than 85\%) of developers considered
the ability of a localization tool to provide a \emph{rationale} or
reason for a localization important.  A mutation plus the tests that
stop failing when it is applied is a practical, concrete explanation
of a fault localization.

### 2016-12-19 metrics.tex
ready submit
more fixes and such

For every failing test case, its response to mutants defines a bit-vector, with
length equal to the number of mutants that repaired any test case,
where a 1 bit indicates that the mutant in question repairs this test
case.  These cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   Hamming distance for the first pair of tests is twice as
large, despite the fact we have no evidence $t_1'$ and
$t_2'$ are due to the same fault, in contrast to strong evidence for
$t_1$ and $t_2$.  A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.

@@

In Section \ref{conc} we briefly discuss possible uses of $d$
requiring comparison of both failing and passing test cases. The only
change required is to use three-valued vectors, where 1 indicates a failing property succeeds and -1 indicates a succeeding property fails.

>>>>

For every failing test case, its response to mutants defines a bit-vector, with
length equal to the number of mutants that repaired any test case,
where a 1 bit indicates that the mutant in question repairs this test
case.  These cannot be effectively compared with Hamming distance. Consider $t_1$ and $t_2$, both repaired
by 100 mutants.  If these two test cases share 90 common repairing
mutants, and disagree for 10, they have a Hamming
distance of 20.  This makes them ``less similar'' than two test cases,
$t_1'$ and $t_2'$, where $t_1'$ is repaired by 5 mutants, $t_2'$ is
repaired by 5 mutants, and \emph{none of those mutants overlap.}   A Jaccard distance, also used (as similarity) in some fault
localization algorithms \cite{Pinpoint}, is a better fit.  For bitvectors $u$ and $v$ of length $n$:
%\vspace{-0.08in}
\[d(u,v) = 
\begin{cases}
\frac{\sum_{i=0}^{n-1} 1\ \text{if}\ u_i \neq v_i\ \text{else}\ 0}{\sum_{i=0}^{n-1} 1
\  \text{if}\ u_i \neq 0 \vee v_i \neq 0\ \text{else}\ 0} & \exists i:u_i\neq 0 \vee v_i\neq 0\\
0 & otherwise
\end{cases}
\]

This metric, the portion of mismatches over bits that are 1 in either
vector, matches our intuitions about the above comparisons\footnote{In Section \ref{conc} we discuss possible uses of $d$
requiring comparison of both failing and passing test cases:  in this 
case, we would use three-valued vectors, where 1 indicates a 
failing property succeeds and -1 that a succeeding property 
fails.}.  It
essentially formalizes the intuition of the onion-ring model, where
more matching repairs indicates a much higher probability two failures
are due to the same fault, even if not all repairs match.

@@

### 2016-12-19 relatedwork.tex
fix for double blind
more fixes and such

The most closely related work is that of Chen et. al \cite{PLDI13} (which shares one author with the present paper).  We use two of the same compiler data sets, and both apply the FPF \cite{Gonzalez} algorithm.  The distance metrics used with FPF in the previous work, however, were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper uses the FPF approach in the context of a more principled causal comparison of program executions that applies in theory to any executions, not just failing test cases, and introduces novel fault localizations.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  The work of Chen et. al \cite{PLDI13} provides an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.

>>>>

The most closely related work is that of Chen et. al \cite{PLDI13}.  We use two of the same compiler data sets, and both apply the FPF \cite{Gonzalez} algorithm.  The distance metrics used with FPF in the previous work, however, were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper uses the FPF approach in the context of a more principled causal comparison of program executions that applies in theory to any executions, not just failing test cases, and introduces novel fault localizations.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  Chen et. al \cite{PLDI13} provide an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.
